\documentclass{beamer}
\usetheme{Copenhagen}
\usepackage{multicol}
\usepackage{graphicx}
\title{Jumping Man: A CS251 Project by Group 27}
\author[shortname]{Lohith R\\140050041\\lohithravuru@gmail.com\\ \inst \and Nihal P\\140050062\\nihal1729@gmail.com\\ \and Jagadeesh B\\140050053\\jagadeeshboddeda649@gmail.com\\  }
\institute{IITB}
\date{\today}

\newcommand\myheading[1]{%
  \par\bigskip
  {\Large\bfseries#1}\par\smallskip}

\begin{document}
\frame{\titlepage}
\frame{
\frametitle{Idea and Motivation}
 \begin{block}{Motivation:}
 We want to build a game which resembles nearly to the present android games
which are growing a lot these days.
 \end{block}
 \begin{block}{Idea}
  We are hoping to build a small Box2D game similar to the Mr.Jump game in itunes.\\
It consists a minimum of 10 elements as part of the game and we will decide
the levels according to the time available for us.It is basically a typical game like mario,in
which the player has to move front without hitting any obstrucles and has some
power elements as he passes through the game.
\end{block}
% \begin{enumerate}
% \item Introduction
% \item How to make title page
% \item Understanding of latex
% \end{enumerate}
}
\begin{frame}{Only one frame}
\frametitle{Interesting Features of the Game}
\begin{block}{Powerups}
\setbeamertemplate{itemize items}[default]
\begin{itemize}
\item<1-> The square powerup.
\item<2-> The rhombus powerup.
\item<3-> The rocket powerup.
\item<4-> The gate opener.
\end{itemize}
\end{block}

\begin{block}{Obstrucles}
\setbeamertemplate{itemize items}[default]
\begin{itemize}
\item<5-> The triangle killer.
\end{itemize}
\end{block}

\end{frame}

\begin{frame}[fragile]
\frametitle{Ideas for future Updates}
\setbeamertemplate{itemize items}[default]
\begin{enumerate}
\item <1-> Make the Graphical User Interface more attractive
\item <2-> Increase the number of levels
\item <3-> Include some sound effects
\item <4-> Remove the minor bugs and make the code perfect
\item <5-> Create a well-defined game design.  
\end{enumerate}
\end{frame}
\end{document}




